\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-12 WOOT/Files/experiment.tex
[experiment] case study of qr code payment

Remote control mode is ideal for the attacker to control the victim's devices and grab all information shown on the victim's devices. However, if the attacker wants to control with video stream indicated, it requires high power consumption to encode video streams and stable network connections. In the real world, high power consumption will increase the posibilities of being noticed by the victim, and stable network connections is hardly guaranteed.

\yechang{Unlock status is needed or not?}
\hongyi{Needed}

@@

@@

>>>>

Remote control mode is ideal for the attacker to control the victim's devices and grab all information shown on the victim's devices. However, it needs user consent for the first time and requires high power consumption to encode video streams and stable network connections.
In the real world, high power consumption will increase the posibilities of being noticed by the victim, and stable network connections is hardly guaranteed.

@@

\subsubsection{Case study of QR code payment}

QR code payment is a payment method where payment is typically performed as the following steps:
\ding{182} The payer opens the payment application on his/her mobile device, and present his/her payment QR code to the payee. This QR code is encoded with a globally unique ID to identify the payer's account. 
\ding{183} The payee scan the payment QR code presented by the payer. By presenting this QR code, the payer authorizes proceeding with the payment.
\ding{184} An order generated by this scan is sent to the payment service provider. Then the payment service provider requests the payer to confirm the transaction.
\ding{185} After confirmation, the payment service provider proceed with this transaction and return the payment result to both the payee and the payer.

In the real-world, some payment service providers provide special rules for micropayments purchases. A micropayment is pre-determined by the payment service provider with thresholds in the user agreement. For example, WeChat Pay regards payments less than CNY \textyen 1000 as micropayments. Differing from a typical payment procedure, when micropayments are made, confirmations can be applied automatically without requiring the payer to take further action, which is often encouraged by the payment service provider.

The payment QR code is associated with the payer's account. If a victim's payment code is leaked to an attacker, an attacker can use the victim's payment code to proceed with payments. Furthermore, the attacker can use several micropayments to steal money from the victim's account while leaving the victim unconscious. In summary, the payment QR code is highly sensitive on users' devices.

@@

\subsection{evaluation}

\begin{table*}
	\centering
	\begin{tabular}{|c|c|c|c|c|}
		\hline
		Application Column  & Application & Private information leaked                       \\
		\hline
		Finance App         & Alipay      & Alipay account, personal assets(blance)          \\
		\hline
		Social  Finance App & WeChat      & WeChat account, blance, chat history             \\
		\hline
		Social App          & QQ          & QQ account, interpersonal nexus, chat history    \\
		\hline
		Social App          & Twitter     & Twitter account, interpersonal nexus             \\
		\hline
		Social App          & Gmail       & Gmail account, mail records                      \\
		\hline
		Finance App         & ICBC        & ICBC account, password, personal assets(blance)  \\
		\hline
		Finance App         & Paypal      & Paypal account, blance, bank accounts            \\
		\hline
		Tool                & Chrome      & Sites visited                                    \\
		\hline
		Tool                & Health      & personal physical metrics      					 \\
		\hline
	\end{tabular}
	\linebreak
	\caption{Information extracted}
	\label{table:information_extracted}
\end{table*}
